### 2017-01-04 paper/evaluation.tex
Remainders....

@@

>>>>

\Jbc{Ensure to describe that: I re-executed the experiment 3 times (1
remaining!), subjects that could not run the tests due to incompatible
testing environment were removed (likely to happen for subjects that
rely on database systems and other external factors), the exit status
for all executions are consistent and removed the unstable subjects
(flakiness)}

@@

\Jbc{I will rework the results and plots}
